\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-09-28 paper/manuscript.tex
added a paragraph to the conclusion with a bit of bragging about the scaleability of our approach

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis. The methods involved in the pipeline include checking the integrity of the site addresses, extracting English language from website contents, identifying document types, and removing boilerplate language. Government website contents can, and have been, used to study questions related representation, government transparency, and public policy priorities. The methods we develop can be used to scale up projects involving website data collection by automating the process. Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government. We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.

>>>>

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis. The methods involved in the pipeline include checking the integrity of the site addresses, extracting English language from website contents, identifying document types, and removing boilerplate language. Government website contents can, and have been, used to study questions related representation, government transparency, and public policy priorities. The methods we develop can be used to scale up projects involving website data collection by automating the process.

In terms of pure scope, our method is superior to the existing approaches. Manual content analysis (see, for example, \cite{Druckman2009}) relies on research assistants reading and evaluating websites, and therefore might struggle to provide a complete understanding of even individual websites, which often contain thousands of pages. Scrapers conventionally used in the social sciences (see, for example, \citealt{Cryer2017}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one. By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space. Consequently, our approach facilitates the kind of bulk data collection and analysis necessitated by an ever-growing web.

Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government. We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
